Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-03-28 paper/AlignedIsotropicGW.tex
Added Christopher Berry to acknowledgements.
Changed title to make shorter (~90 characters based on Nature limits).

\title{Distinguishing Between Spin-Aligned and Isotropic Binary Black
  Hole Populations Using Gravitational Wave Observations}

@@

We thank Richard O’Shaughnessy for comments on this work.

>>>>

\title{Distinguishing Spin-Aligned and Isotropic Black Hole
  Populations With Gravitational Waves}

@@

We thank Richard O’Shaughnessy and Christopher Berry for discussions
comments on this work.
